Title

### 2023-09-16 Tareas por hacer.tex
Algunos cambios mas

\begin{itemize}
\item \textbf{Efficient universal quantum channel simulation in IBM's cloud quantum computer (Shi-Jie Wei, Tao Xin, Gui-Lu long) Science China:}\\

>>>>

\begin{itemize}
\item \textbf{Quantum Simulation of Open Quantum Systems Using Density-Matrix Purification (Anthony W. Schlimgen et al.) PRL
} \\

With the increased
use of quantum algorithms for unitary-gate-based quantum
computers, techniques for casting non-unitary operations into
unitary forms have become increasingly important.

\item  \textbf{Quantum Simulation of Open Quantum Systems Using a Unitary Decomposition of Operators (Anthony W. Schlimgen, et al.) PRL:}

The time evolution of an electronic state is
critical to predicting many important physical phenomena
including exciton transport [1], molecular conductivity [2],
chemical catalysis [3], quantum phase transitions [4, 5], and
magnetization [6]. Often these processes involve non-trivial
interactions with a large environment, requiring the definition and treatment of open quantum systems [7–15]. Recent
research has considered the simulation of open quantum systems on quantum devices [16–20].

\item \textbf{Efficient universal quantum channel simulation in IBM's cloud quantum computer (Shi-Jie Wei, Tao Xin, Gui-Lu long) Science China:}\\
